\chapter*{Acknowledgements}\addcontentsline{toc}{chapter}{Acknowledgements}

These six years that I spent in Uppsala, first as an Erasmus student and then as
a PhD student, were some of the best ones in my life. All the new things that I
experienced and the different people that supported me during this time are the
reason for it. 
\vspace{0.5cm}

\noindent
I would like to thank my supervisor, Janos, for first bringing me into the group during my
exchange period and then offering me the opportunity to do this PhD, as well as
always giving me the freedom to work in what I find interesting. Also many 
thanks to both Janos and Inger for several amazing sailing trips during some
glorious summer weekends.
\vspace{0.5cm}

\noindent
To my co-supervisor David I am very grateful for the constant support, including
helping me write my first paper, inspiring discussions during lunch time
which helped me solve problem after problem, as well as continuous encouragement to
publish my ideas.
\vspace{0.5cm}

\noindent
I would also like to thank:
\vspace{0.5cm}

\noindent
Nic, for never being quiet and for all the assistance with my math difficulties.
\vspace{0.5cm}

\noindent
Abraham and Hanna, for all the guidance, specially in the beginning,  and for all
the insightful conversations and new interesting ideas that you introduced me
to.
\vspace{0.5cm}

\noindent
Tomas, for always listening to all my silly questions, for countless hours of great
discussions in front of the blackboard, even when the computers were working,
and for being a fantastic office-mate.
\vspace{0.5cm}
 
\noindent
G\"osta, for introducing me to diffractive imaging, Ultimate Frisbee games and for a memorable trip to California.
\vspace{0.5cm}

\noindent
Calle, for inspiring me to finish my PhD.
\vspace{0.5cm}

\noindent
Michiel, Pavel, Pavel, Anne and Rafal for many hours of card playing and good fun.
\vspace{0.5cm}

\noindent
Tiago, for an unforgettable first six months.
\vspace{0.5cm}

\noindent
Elsa, Daniel, for giving me the opportunity to practise Portuguese.
\vspace{0.5cm}

\noindent
Magnus, Alexandra, Sara, Johan, Erik, Marvin, Martin, Gunilla, Karin,
Daniel, Bianca, Malin, Du\v{s}ko, Daniel, Jakob, Jochen, Olof for the fun company during
fika and for making a terrific lab.
\vspace{0.5cm}

\noindent 
The great bunch of guys from Flogsta building 5 second floor during the fall of
2004, for keeping me up during a harsh winter.
\vspace{0.5cm}
 
\noindent
All the exchange students in the D\"obelnsgatan exchange student corridor between 
2005 and 2007, for the warm company and happy parties.
\vspace{0.5cm}
 
\noindent
To allihopa@xray, for creating a pleasant working environment.
\vspace{0.5cm}

\noindent
To all the administrative personal at ICM, particularly Sigrid, for always
taking care of any problems.
\vspace{0.5cm}

\noindent
To everyone at the FLASH and LCLS beamtimes, for making them more enjoyable.
\vspace{0.5cm}

\noindent
All my co-authors, it was a pleasure and an honour to work with you all.
\vspace{0.5cm}

\noindent
My family for the immense support and encouragement you have given me
throughout all these years.
\vspace{0.5cm}

\noindent
To Au\v{s}ra, for making me the happiest person in the world.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Thesis"
%%% End: 
