\chapter{The author's contribution}

\section*{Publications included in this thesis}

\vspace{1cm}

\subsection*{Paper \ref{cowboys}:}{\bf H. Chapman et al. \noindent
{\em ``Femtosecond diffractive imaging with a soft-X-ray free-electron laser''}}

\noindent
I was involved in the data analysis and image reconstruction.

\noindent
\subsection*{Paper \ref{melting}:}{\bf D. van der Spoel et al. {\em ``
 Structural studies of melting on the picosecond time scale''}}

\noindent I did all the X-ray diffraction calculations and the large parts of
the writing related to it.

\noindent
\subsection*{Paper \ref{music}:}{\bf A. Ravasio et al. {\em `` 
Single-Shot Diffractive Imaging with a Table-Top
      Femtosecond Soft X-Ray Laser-Harmonics Source''}}

\noindent I did all the data analysis and  image reconstructions. I was involved
in writing the corresponding sections of the paper.

\noindent
\subsection*{Paper \ref{dynamics}:}{\bf F. R. N. C. Maia et al. {\em ``Structural variability and the incoherent addition of scattered
      intensities in single-particle diffraction''}}

\noindent The idea was generated from my observations of previous reconstruction
projects. I did all the diffraction simulations and image reconstruction as well
as most of the analysis and writing of the paper.

\clearpage

\subsection*{Paper \ref{hawk}:}{\bf F. R. N. C. Maia et al. {\em ``Hawk: the image reconstruction package for coherent X-ray diffractive
      imaging''}}

\noindent I coded most of the software and wrote a large majority of the paper.

\section*{Supporting publications}

\vspace{1cm}

\subsection*{Paper \ref{QRB}:}{\bf M. Bergh et al. {\em ``Feasibility of imaging living cells at subnanometer resolutions by ultrafast X-ray diffraction'' }}

\noindent I contributed to the calculations and writing of section on depth information from diffraction
experiments.
\subsection*{Paper \ref{nano}:}{\bf M. J. Bogan et al. {\em ``Single particle X-ray diffractive imaging''}}

\noindent I was involved in the preparation and implementation of the experiment
at FLASH as well as data analysys and image reconstruction.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Thesis"
%%% End: 
