\chapter{Introduction}\label{introduction}\noindent

``The history of the living world can be summarized as the elaboration of ever
more perfect eyes within a cosmos in which there is always something more to be
seen'' wrote Pierre Teilhard de Chardin in {\em The Phenomenon of Man} (1955). In the
early sixteen hundreds, members of the Accademia dei Lincei in Rome decided to
split the task of exploring the world around us: Gallileo was to study things
big while Stelluti and Cesi were to explore the microscopic world. 300 yeares
later, a fundamental barrier was taken down through the invention of X-ray
crystallography, which made it possible to observe structures much smaller than
the wavelength of visible light.

X-ray crystallography is one of the most successful techniques ever developed
for the study of structures in atomic details. It has had a huge impact on
biology, e.g. through the discovery of the structure of DNA, RNA, proteins
and their complexes. Every year thousands of new structures are solved and
deposited in the Protein Data Bank. Cryo electron microscopy also shows great
promise with current structures frequently achieving resolutions below 10 \AA,
but still not enough for atomic resolution. 

% Mankind has always had a fascination with looking at the infinitely
% small. Since the invention of microscope people have been trying to find ways to
% look at smaller and smaller things. The invention of X-ray crystallography in
% the beginning of the twentieth century made it possible to observe the
% structures of things much smaller than the wavelength of visible light.

% Nowadays X-ray crystallography is one of the most successful structural techniques ever
% developed, and for instance in biology, every year thousands of new protein structures are solved and deposited
% in the Protein Data Bank. It is currently the only technique capable of
% delivering atomic resolution images of biological macromolecules. Cryo electron microscopy also shows great promise with current
% structures frequently achieving resolutions below 10 \AA, but still not enough
% for revealing atomic details.

However, X-ray crystallography, as the name suggests, is limited to systems that
can be crystallized. Many, if not most, systems of biological interest are very
difficult, or impossible to crystallize. Probably the most striking example is
that of a simple cell, but there are many others such as organelles, glycoproteins and many
membrane proteins. Alternative approaches have to be employed to image these
samples.

% , including cryo electron microscopy, atomic force microscopy or
% transmission electron microscopy. Unfortunately all of these alternatives have
% serious drawbacks compared to X-ray crystallography such as not being able to
% image the interior of large samples, providing a lower resolution or requiring
% fixing, sectioning or staining of the sample.

Ultrafast Coherent X-ray Diffractive Imaging (CXDI) is a relatively new
technique, which uses a coherent, short and extremely
bright pulse of X-rays to capture a diffraction image of the sample which is
then phased to reveal the sample structure. CXDI has the potential to allow three
dimensional imaging of nonperiodic reproducible biological samples up to atomic
resolution and two dimensional imaging of non reproducible samples up to
very high resolution, without the need of modifying the sample.

% It doesn't necessarily require short pulses
%CXDI requires extremely intense X-ray pulses as it does not benefict from the
%amplification effect of a crystal as X-ray crystallography does. But on the
CXDI does not benefict from the
amplification effect of a crystal as X-ray crystallography does. But on the
other hand it is possible to sample the diffraction pattern continuously which
makes the phasing problem much simpler. To be able to achieve high 
resolution using CXDI, very short and intense pulses are necessary otherwise the radiation
damage that develops during the exposure limits the maximum resolution. For
example, the highest resolution possible for biological samples using current
synchrotron based x-ray microscopes is around 20nm, limited by radiation
damage \cite{Howells2009Assessment}.

The recent development of X-ray free-electron lasers (FELs) gives a perfect
instrument to realize the full potential of CXDI. X-ray FELs can produce extremely
intense X-ray pulses, a billion times more brilliant than third
generation synchrotron sources. X-ray FEL pulses are also extremely short, on the order of
only a few femtoseconds. FLASH, in Hamburg, Germany, was the first soft X-ray
free electron laser in the world, and is based on the Self Amplified Spontaneous
Emission (SASE) principle. It started operations in the summer of 2005 at
a wavelength of 32nm and a peak power on the order of gigawatts and pulse length as
short as 10fs. It has gone through several updates reaching the wavelength of
6.5nm. FLASH is a test facility for the European X-ray Free Electron
Laser (XFEL), and it has produced many important results in the CXDI field \cite{Chapman2006Femtosecond,Chapman2007Femtosecond}. In April 2009 the Linac Coherent Light Source (LCLS)
became the first hard X-ray free electron laser in the world producing light
with a wavelength of \mbox{1.5 \AA}. The Spring-8 Compact SASE Source (SCSS) in
Japan will soon be ready and the XFEL will follow in a few years.

During the last few years there has also been a rapid development of tabletop
high harmonic generation (HHG) sources. These have the potential to compete one
day with free electron lasers and they are much more affordable for
individual labs. Nowadays there are HHG sources with very good coherence
properties capable of producing extremely short pulses, under 1fs, at soft X-ray wavelengths and more than $10^{11}$ photons
per pulse \cite{Ravasio2009SingleShot}. This is still a few orders of magnitude below what is
possible using accelerator-based FELs but progress is fast, and those sources
might
% due to the lower cost and greater access they might
become very important tools in the near future.

The availability in the near future of several hard X-ray FELs combined with the
increasing development of CXDI experimental techniques and data processing
algorithms have the potential to transform Ultrafast Coherent X-ray Diffractive
Imaging from a niche of unconventional techniques into a mainstream structural
biology tool that complements X-ray crystallography or electron microscopy.


%I'm pretty sure i need to reformulate this 
The aims of this thesis are: to present recent experimental results in Ultrafast
Coherent X-ray Diffractive Imaging using both free electron lasers and
optically-driven table-top X-ray laser, to theoretically investigate the problem of sample heterogeneity
for reproducible samples and to propose new experiments made possible with these
new sources.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Thesis"
%%% End: 
